Fusion Moves for Correlation Clustering

### 2014-11-11 paper/egpaper_for_review.tex
test

>>>>

%%%%%%global tikz styles

\tikzstyle{eBlack}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=black!70!black, font=\small,align=left, line width=1mm]
\tikzstyle{eNotCut}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=green!70!black, font=\small,align=left, line width=1mm]
\tikzstyle{eBlue}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=blue!70!black, font=\small,align=left, line width=1mm]
\tikzstyle{eCut}=[very thick,dotted,minimum size = 0.5cm,inner sep = 0pt,draw=black, font=\small,align=left, draw=red!70!black, line width=1mm]
